---
title: "MGSC 661 - Midterm Project"
output:
  pdf_document: default
  html_notebook: default
---

# Importing libraries and data

```{r include=FALSE}
Sys.setlocale("LC_ALL", "C")
require(visreg)
require(glue)
require(car)
require(lmtest)
require(splines)
require(psych)
require(stargazer)
require(plm)
require(ggplot2)
require(ggtext)
require(ggpubr)
require(ggrepel)
require(ggthemes)
require(scales)
require(caTools)
require(methods)
require(boot)
require(tidyverse)
require(dplyr)
require(glue)
require(GGally)
require(broom)


windowsFonts(Helvetica = "Product Sans")
```

```{r}
theme_lox <- function() {
  theme(
    panel.grid.major.x = element_line(linewidth = 0.3, colour = "#cbcbcb"),
    panel.grid.major.y = element_line(linewidth = 0.3, colour = "#cbcbcb"),
    plot.title = element_markdown(
      family = "Helvetica",
      size = 22,
      face = "bold",
      color = "#222222"
    ),
    plot.subtitle = element_text(
      family = "Helvetica",
      size = 16,
      margin = margin(2, 0, 2, 0)
    ),
    plot.caption = element_text(family = "Helvetica", face = "bold"),
    axis.text = element_text(
      family = "Helvetica",
      size = 12,
      color = "#222222"
    ),
    axis.title = element_text(
      family = "Helvetica",
      size = 14,
      color = "#222222"
    ),
    legend.text = element_text(family = "Helvetica", size = 12),
    legend.title = element_text(
      family = "Helvetica",
      size = 14,
      face = "bold"
    ),
    legend.position = "right",
    strip.text = element_text(
      family = "Helvetica",
      size = 12,
      hjust = 0.5
    )
  )
}
```

```{r}
data <- read.csv("./IMDB_data_Fall_2023.csv")
```

# Exploratory data analysis

```{r}
head(data)
summary(data)
```

### IMDB Score

```{r fig.width=15, fig.height=8}
ggplot(data, aes(x = imdb_score)) +
  geom_histogram(binwidth = 1, fill = '#008FD5', color='black') +
  scale_fill_fivethirtyeight() +
  scale_x_continuous(breaks = breaks_width(width = 1)) +
  labs(x = "IMDb Score", y = "Number of movies", title = "Distribution of IMDB Score") +
  theme_pubr() +
  theme_lox()

ggsave(filename = "plots/imdb_score.png", device = "png")
```

### Movie budget

```{r fig.width=12, fig.height=8}
ggplot(data, aes(x = movie_budget)) +
  geom_histogram(bins = 10, fill = "#008FD5", color = "black") +
  scale_x_continuous(breaks = breaks_pretty(), labels = label_dollar(scale_cut = cut_short_scale())) +
  labs(x = "Movie budget", y = "Number of movies", title = "Distribution of movie budget") +
  theme_pubr() +
  theme_lox()

ggsave(filename = "plots/movie_budget.png", device = "png")
```

### Release year

```{r fig.width=12, fig.height=8}
ggplot(data, aes(x = release_year)) +
  geom_histogram(bins = 10, fill = "#008FD5", color="black") +
  scale_x_continuous(breaks = breaks_pretty(n = 10)) +
  labs(x = "Release Year", y = "Number of movies", title = "Distribution of release year") +
  theme_pubr() +
  theme_lox()

ggsave(filename = "plots/release_year.png", device = "png")
```

### Release month

```{r fig.width=12, fig.height=8}
ggplot(data, aes(x = factor(release_month,levels = month.abb))) +
  geom_bar(aes(fill = release_month), color = "black") +
  guides(fill="none") +
  scale_fill_tableau(palette = "Tableau 20") +
  labs(x = "Release Month", y = "Number of movies", title = "Number of movies by release month") +
  theme_pubr() +
  theme_lox() +
  theme(panel.grid.major.x = element_blank())
  
ggsave(filename = "plots/release_month.png", device = "png")
```

### Number of faces

```{r fig.width=12, fig.height=8}
ggplot(data, aes(x = nb_faces)) +
  geom_histogram(bins = 10, fill = "#008FD5", color = "black") +
  scale_x_continuous(breaks = breaks_pretty()) +
  labs(x = "Number of faces", y = "Number of movies", title = "Distribution of number of faces in the movie poster") +
  theme_pubr() +
  theme_lox()

ggsave(filename = "plots/number_faces.png", device = "png")
```

### Duration

```{r fig.width=12, fig.height=8}
ggplot(data, aes(x = duration)) +
  geom_boxplot(outlier.size = 4) +
  scale_x_continuous(breaks = breaks_pretty()) +
  labs(x = "Duration", title = "Boxplot of movie duration") +
  theme_pubr() +
  theme_lox() +
  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank())

ggsave(filename = "plots/duration.png", device = "png")
```

## Bivariate distributions

### Movie budget ~ IMDB Score

```{r fig.width=12, fig.height=8}
ggplot(data, aes(x = movie_budget, y = imdb_score)) +
  geom_point() +
  geom_text_repel(aes(label = movie_title), size = 5, max.overlaps = 2, nudge_y = 0.5) +
  scale_x_continuous(breaks = breaks_pretty(n=10), labels = label_dollar(scale_cut = cut_short_scale())) +
  labs(x = "Movie budget", y = "IMDb Score", title = "Movie budget and IMDb score") +
  theme_pubr() +
  theme_lox()

ggsave(filename = "plots/movie_budget_imdb_score.png", device = "png")
```

### Duration ~ IMDB Score

```{r fig.width=12, fig.height=8}
ggplot(data, aes(x = duration, y = imdb_score)) +
  geom_point() +
  geom_text_repel(aes(label = movie_title), size = 5, max.overlaps = 3, nudge_y = 0.5) +
  scale_x_continuous(breaks = breaks_pretty(n=10), labels = label_number()) +
  labs(x = "Duration", y = "IMDb Score", title = "Movie duration and IMDb score") +
  theme_pubr() +
  theme_lox()

ggsave(filename = "plots/duration_imdb_score.png", device = "png")
```

### Genre ~ IMDB Score

```{r fig.width=12, fig.height=8}
data %>%
  select(movie_id, movie_title, imdb_score, action:crime) %>%
  pivot_longer(cols = c(-imdb_score, -movie_id, -movie_title), names_to = "genre") %>%
  mutate(genre = str_to_sentence(genre)) %>%
  group_by(genre) %>%
  filter(value == 1) %>%
  ggplot(aes(x = genre, y = imdb_score, fill = genre)) +
  geom_boxplot() +
  scale_fill_tableau(palette = "Tableau 20") +
  scale_y_continuous(breaks = breaks_pretty(n = 10), limits = c(0, 10)) +
  guides(fill = "none") +
  labs(x = "Genre", y = "IMDb Score", title = "Boxplot of IMDb score by genre", subtitle = "Movies span across genres") +
  theme_pubr() +
  theme_lox()

ggsave(filename = "plots/genre_imdb_score.png", device = "png")
```

### Release Month ~ IMDB Score

```{r fig.width=12, fig.height=8}
data %>%
  mutate(release_date = dmy(str_c(release_day, release_month, release_year, sep = "-"))) %>%
  mutate(release_month = month(release_date, label = TRUE)) %>%
  ggplot(aes(x = release_month, y = imdb_score, fill = release_month)) +
  geom_boxplot(outlier.size = 2) +
  geom_text_repel(aes(label = movie_title), max.overlaps = 3, size = 4) +
  scale_fill_tableau(palette = "Tableau 20") +
  scale_y_continuous(breaks = breaks_pretty(n=10), limits = c(0, 10)) +
  guides(fill = "none") +
  labs(x = "Release Month", y = "IMDb Score", title = "Boxplot of IMDb score by release month") +
  theme_pubr() +
  theme_lox()

ggsave(filename = "plots/release_month_imdb_score.png", device = "png")
```

### Actor 1 ~ IMDB Score

```{r fig.width=12, fig.height=8}
data %>%
  filter(actor1 %in% (
    data %>%
      group_by(actor1) %>%
      count(sort = TRUE) %>%
      head(10)
  )$actor1) %>%
  ggplot(aes(
    x = fct_reorder(actor1, imdb_score, .fun = median),
    y = imdb_score,
    fill = actor1
  )) +
  geom_boxplot(outlier.size = 2) +
  geom_text_repel(aes(label = movie_title), max.overlaps = 2, size = 4) +
  scale_fill_tableau(palette = "Tableau 20") +
  scale_y_continuous(breaks = breaks_pretty(n=10), limits = c(0, 10)) +
  guides(fill = "none") +
  labs(
    x = "Actor 1 Name",
    y = "IMDb Score",
    title = "Boxplot of IMDb score by Actor 1",
    subtitle = "Top 10 actors by number of movies shown"
  ) +
  theme_pubr() +
  theme_lox()

ggsave(filename = "plots/actor1_imdb_score.png", device = "png")
```

### Distributor ~ IMDB Score

```{r fig.width=12, fig.height=8}
data %>%
  filter(distributor %in%
           (data %>%
              group_by(distributor) %>%
              count(sort = TRUE) %>%
              head(10))$distributor) %>%
  ggplot(aes(x = distributor, y = imdb_score, fill = distributor)) +
  geom_boxplot(outlier.size = 2) +
  geom_text_repel(aes(label = movie_title), max.overlaps = 2, size = 4) +
  scale_fill_tableau(palette = "Tableau 20") +
  scale_y_continuous(breaks = breaks_pretty(n=10), limits = c(0, 10)) +
  guides(fill = "none") +
  labs(
    x = "Distributor",
    y = "IMDb Score",
    title = "Boxplot of IMDb score by distributor",
    subtitle = "Top 10 distributors by number of movies shown"
  ) +
  theme_pubr() +
  theme_lox() +
  coord_flip()

ggsave(filename = "plots/distributor_imdb_score.png", device = "png")
```

# Data preprocessing

## Checking data types

```{r}
data %>% str()
```

```{r}
data_cleaned <- data %>%
  mutate(across(
    .cols = c(
      'language',
      'country',
      'maturity_rating',
      'aspect_ratio',
      'distributor',
      'director',
      'colour_film',
      'cinematographer',
      'production_company'
    ),
    ~ factor(.x)
  ))

data_cleaned <- data_cleaned %>%
  mutate(release_month = month(fast_strptime(release_month, format = "%b"), label =
                                 TRUE)) %>%
  mutate(release_month = factor(release_month, levels = month.abb, ordered = FALSE))
```


## Standardizing numerical columns
```{r}
data_cleaned <- data_cleaned %>%
  mutate(across(
    .cols = c(
      "movie_budget",
      'duration',
      'nb_news_articles',
      'actor1_star_meter',
      'actor2_star_meter',
      'actor3_star_meter',
      'nb_faces',
      'movie_meter_IMDBpro'
    ),
    .fns = ~ scale(.) %>% as.vector()
  ))
```

## Feature engineering

### Checking levels for categorical columns

```{r}
categorical_columns <- data_cleaned %>%
  summarize(across(where(is.factor), ~nlevels(.x))) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "num_levels")

categorical_columns
```

We see that director, cinematographer, and production company have a lot of unique values. A priori, we expect to drop these columns when building the model.

Let us check the counts for the other variables

```{r}
categorical_columns %>% 
  filter(!variable %in% c("director", "cinematographer", "production_company")) %>%
  pull(variable) %>%
  walk(
    ~ data_cleaned %>%
      group_by_at(.x) %>%
      count(sort = TRUE) %>%
      print()
  )
    
```

We see that:

-   The language is primarily "English"
-   The country is primarily "USA"
-   The films are primarily "Color"

These features can also be dropped when building the model.

Further:
-   The aspect ratios are primarily "2.35" or "1.85"
-   The maturity ratings are primarily "R", "PG-13", "PG" or "G"

For these features, rows containing values apart from the ones specified above can be lumped into an "Other" category.

For distributor and plot keywords, we can create binary features for the top 10 values by count.

### Lumping factors into "Others"
```{r}
data_cleaned <- data_cleaned %>% mutate(
  aspect_ratio = fct_lump_n(aspect_ratio, n = 3),
  maturity_rating = fct_lump_n(maturity_rating, n = 5)
)
```


### Top 10 keywords

```{r}
top_10_keywords <- data_cleaned %>%
  select(plot_keywords) %>%
  separate_longer_delim(cols = "plot_keywords", delim = "|") %>%
  group_by(plot_keywords) %>%
  count(sort = TRUE) %>%
  head(10)

for (keyword in top_10_keywords$plot_keywords) {
  col_name <- glue("plot_{keyword}")
  data_cleaned[[col_name]] <-
    as.integer(lapply(data_cleaned$plot_keywords, function (x) {
      str_detect(x, keyword)
    }))
}
```

### Top 5 distributors

```{r}
top_5_distributors <- data_cleaned %>%
  select(distributor) %>%
  separate_longer_delim(cols = "distributor", delim = "|") %>%
  group_by(distributor) %>%
  count(sort = TRUE) %>%
  head(5)

for (distributor in top_5_distributors$distributor) {
  col_name <- glue("distributor_{distributor}")
  data_cleaned[[col_name]] <-
    as.integer(lapply(data_cleaned$distributor, function (x) {
      str_detect(x, distributor)
    }))
}
```

## Checking heteroscedasticity and linearity
```{r fig.width=12, fig.height=8}
numerical_predictors <-
  c(
    "movie_budget",
    "duration",
    "nb_news_articles",
    "nb_faces",
    "actor1_star_meter",
    "actor2_star_meter",
    "actor3_star_meter",
    "movie_meter_IMDBpro"
  )

for (predictor in numerical_predictors) {

  print(glue("Running checks for: ", predictor))

  # Run linear model
  lin_reg_predictor <-
    lm(formula(paste("imdb_score ~", predictor)), data = data_cleaned)
  
  print(summary(lin_reg_predictor))
  # Run non-constant variance test
  print(ncvTest(lin_reg_predictor))
  
  
  # Generate a scatterplot
  print(
    ggplot(data, aes(
      x = !!sym(predictor), y = imdb_score
    )) +
      geom_point() +
      geom_smooth(method = lm) +
      scale_x_continuous(breaks = breaks_pretty()) +
      labs(y = "IMDb Score",
           title = paste("IMDb score ~ ", predictor)) +
      theme_pubr() +
      theme_lox()
  )
  
  # Check for linearity
  residualPlots(lin_reg_predictor)
}
```
We see that
- All predictors except the `actor_star_meters` are statistically significant
- `movie_budget`, `duration`, and `movie_meter_IMDBpro` have heteroskedasticity
- `movie_budget` and `nb_faces` are linear, while the other numeric columns are non-linear.


## Checking for multicollinearity
```{r fig.width=12, fig.height=8}
data_cleaned %>%
  select(numerical_predictors) %>%
  cor() %>%
  round(2) %>%
  ggcorr(digits = 2, label = TRUE, label_alpha = 0.5)

ggsave(filename = "plots/corr_plot.png", device = "png")

vif_model <- lm(imdb_score ~ ., data = (data_cleaned %>% select(where(is.numeric))))

vif(vif_model)
```

We see that there is no multicollinearity among the numeric variables in the dataset.

## Removing variables

```{r}
columns_to_remove <-
  c(
    "movie_id",
    "movie_title",
    "imdb_link",
    "actor1",
    "actor2",
    "actor3",
    "genres",
    "release_day",
    "release_year",
    "colour_film",
    "actor1_star_meter",
    "actor2_star_meter",
    "actor3_star_meter",
    "director", 
    "cinematographer", 
    "production_company",
    "language",
    "country",
    "distributor",
    "plot_keywords"
  )

data_cleaned <- data_cleaned %>% select(-all_of(columns_to_remove))
```

```{r}
data_cleaned %>% head()
```

# Model building
## Individual linear regression
```{r}
individual_regressions <- colnames(data_cleaned) %>%
  setdiff("imdb_score") %>%
  syms() %>%
  map(~expr(lm(imdb_score ~ !!.x, data = data_cleaned))) %>%
  map(eval.parent) %>%
  map(tidy) %>%
  bind_rows() %>%
  filter(term != "(Intercept)")
```

```{r}
individual_regressions %>%
  filter(!p.value < 0.05)
```

We see that individually, most of the non-significant predictors (at 5% level) are the dummy variables for release month, genre, plot, and distribution. For completeness, we choose to keep these variables in our model.

```{r fig.width = 15, fig.height = 8}
individual_regressions %>%
  filter(!p.value > 0.05) %>%
  arrange(p.value) %>%
  ggplot(aes(x = fct_reorder(term, -p.value), y = estimate)) +
  geom_col(aes(fill = estimate < 0)) +
  scale_fill_fivethirtyeight() +
  scale_y_continuous(breaks = pretty_breaks(n = 10)) +
  guides(fill = "none") +
  labs(
    x = "Variable",
    y = "Estimate",
    title = "Estimated coefficents for IMDB Score",
    subtitle = "Individual regressions for each variable; Only significant predictors shown (5% level)"
  ) +
  theme_pubr() +
  theme_lox() +
  theme(panel.grid.major.y = element_blank()) +
  coord_flip()

ggsave(filename = "plots/individual_regressions.png", device = "png")
```

## Multiple linear regression
```{r fig.width=12, fig.height=8}
lin_reg_1 <- lm(imdb_score ~ ., data=data_cleaned)
summary(lin_reg_1)
residualPlot(lin_reg_1)
```
### Checking and removing outliers
```{r}
outlierTest(lin_reg_1)

outliers <- names(outlierTest(lin_reg_1)[[1]])
data_cleaned <- data_cleaned %>% filter(!row_number() %in% outliers)
```

### Running the model with outliers removed
```{r fig.width=12, fig.height=8}
lin_reg_2 <- lm(imdb_score ~ ., data=data_cleaned)
summary(lin_reg_2)
residualPlot(lin_reg_2)
```

After removing the outliers, we see that the non-linearity has reduced. Let us now check for heteroskedasticity in the entire model.

### Heteroskedasticity
```{r}
ncvTest(lin_reg_2)
```

Since the model contains heteroskedasticity, we can check the corrected coefficients.
```{r fig.width=12, fig.height=8}
coeftest(lin_reg_2, vcov = vcovHC(lin_reg_2, type = "HC1")) %>% 
  tidy() %>%
  filter(term != "(Intercept)") %>%
  filter(!p.value > 0.05) %>%
  arrange(p.value) %>%
  ggplot(aes(x = fct_reorder(term, -p.value), y = estimate)) +
  geom_col(aes(fill = estimate < 0)) +
  scale_fill_fivethirtyeight() +
  scale_y_continuous(breaks = pretty_breaks(n = 10)) +
  guides(fill = "none") +
  labs(
    x = "Variable",
    y = "Estimate",
    title = "Heteroskedasticity corrected estimated coefficents for IMDB Score",
    subtitle = "Only significant predictors shown (5% level)"
  ) +
  theme_pubr() +
  theme_lox() +
  theme(panel.grid.major.y = element_blank()) +
  coord_flip()

ggsave(filename = "plots/multiple_linear_regression.png", device = "png")
```

### Baseline performance
```{r}
predicted_scores <- predict(lin_reg_2, data_cleaned)
actual_scores <- data_cleaned$imdb_score
mse <- mean((actual_scores - predicted_scores)^2)
rmse <- sqrt(mse)
print(glue("Linear regression MSE: {mse}"))
print(glue("Linear regression RMSE: {rmse}"))
```

## Linear regression - K-fold

To evaluate out-of-sample performance, we use K-fold cross-validation
```{r}
set.seed(420)

lin_reg_k <- glm(imdb_score ~ ., data = data_cleaned)
mse_lin_reg_k <- cv.glm(data_cleaned, lin_reg_k, K = 20)$delta[1]
rmse_lin_reg_k <- sqrt(mse_lin_reg_k)

print(glue("Linear regression MSE: {mse_lin_reg_k}"))
print(glue("Linear regression RMSE: {rmse_lin_reg_k}"))
```

## Polynomial regression

```{r}
set.seed(420)
poly_k_fold_mse <- function(d1, d2, d3, k) {
  poly_k_fold <-
    glm(
      imdb_score ~ movie_budget + poly(duration, d1, raw = d1 == 1) + poly(nb_news_articles, d2, raw = d2 == 1) + poly(movie_meter_IMDBpro, d3, raw = d3 == 1) + . - duration - nb_news_articles - movie_meter_IMDBpro,
      data = data_cleaned
    )
  
  mse_k_fold <- cv.glm(data_cleaned, poly_k_fold, K = k)$delta[1]
  print(glue("MSE for degrees ({d1}, {d2}, {d3}) on {k}-fold CV: {mse_k_fold}"))
  mse_k_fold
}
```

### Finding the optimal degree for numeric features using K-fold CV
```{r warnings=FALSE}
mse_poly_k_fold_df = data.frame(
  i = NA,
  j = NA,
  k = NA,
  mse = NA
)
for (i in 1:5) {
  for (j in 1:5) {
    for (k in 1:5) {
      mse_poly_k_fold_df[nrow(mse_poly_k_fold_df) + 1,] <-
        c(i, j, k, poly_k_fold_mse(i, j, k, 5))
    }
  }
}
```
```{r}
mse_poly_k_fold_df[which.min(mse_poly_k_fold_df$mse), ]
```

### Polynomial regression model with optimal degrees 
```{r}
set.seed(420)
poly_k_fold <- glm(imdb_score ~ movie_budget + poly(duration, 2) + poly(nb_news_articles, 4) + poly(movie_meter_IMDBpro, 5) + . - duration - nb_news_articles - movie_meter_IMDBpro, data = data_cleaned)

mse_poly_k_fold <- cv.glm(data_cleaned, poly_k_fold, K = 20)$delta[1]
rmse_poly_k_fold <- sqrt(mse_poly_k_fold)

print(glue("Polynomial MSE: {mse_poly_k_fold}"))
print(glue("Polynomial RMSE: {rmse_poly_k_fold}"))
```


## Spline regression
### Building the model
```{r}
spline_model_1 <- glm(
  imdb_score ~
    movie_budget +
    bs(
      duration,
      knots = quantile(data_cleaned$duration, c(0.25, 0.5, 0.75)),
      degree = 2
    ) +
    bs(
      nb_news_articles,
      knots = quantile(data_cleaned$nb_news_articles, c(0.25, 0.5, 0.75)),
      degree = 1
    ) +
    bs(
      movie_meter_IMDBpro,
      knots = quantile(data_cleaned$movie_meter_IMDBpro, c(0.25, 0.5, 0.75)),
      degree = 1
    ) + . -movie_budget - duration - nb_news_articles - movie_meter_IMDBpro,
  data = data_cleaned
)
```

### Running K-fold cross-validation
```{r warning=FALSE}
set.seed(420)
mse_spline_k_fold <- cv.glm(data_cleaned, spline_model_1, K = 20)$delta[1]
rmse_spline_k_fold <- sqrt(mse_spline_k_fold)
r_squared_spline_k_fold <- 1 - (spline_model_1$deviance / spline_model_1$null.deviance)

print(glue("Spline MSE: {mse_spline_k_fold}"))
print(glue("Spline RMSE: {rmse_spline_k_fold}"))
print(glue("R-squared: {r_squared_spline_k_fold}"))
```
## Reporting overall performance
```{r warning=FALSE, results='asis'}
performance <-
  data.frame(
    linear=c(
      mse_lin_reg_k,
      rmse_lin_reg_k,
      1 - lin_reg_k$deviance/lin_reg_k$null.deviance,
      length(lin_reg_k$coefficients) - 1
    ),
    poly=c(
      mse_poly_k_fold,
      rmse_poly_k_fold,
      1 - poly_k_fold$deviance/poly_k_fold$null.deviance,
      length(poly_k_fold$coefficients) - 1
    ),
    spline=c(
      mse_spline_k_fold,
      rmse_spline_k_fold,
      1 - spline_model_1$deviance/spline_model_1$null.deviance,
      length(spline_model_1$coefficients) - 1
    )
  )

names(performance) <- c("Linear", "Polynomial", "Spline")
rownames(performance) <- c("MSE", "RMSE", "R^2", "Number of predictors")

stargazer(performance, header = FALSE, digits = 2, type = "latex", out = "tables/model_performance.html", summary = FALSE, title = "Model performance")
```

# Using the models
```{r}
test_data <- read.csv("./test_data_IMDB_Fall_2023.csv")
test_data
```
## Cleaning test data
```{r}
test_data_cleaned <- test_data %>%
  mutate(across(
    .cols = c(
      'language',
      'country',
      'maturity_rating',
      'aspect_ratio',
      'distributor',
      'director',
      'colour_film',
      'cinematographer',
      'production_company'
    ),
    ~ factor(.x)
  ))

test_data_cleaned <- test_data_cleaned %>%
  mutate(release_month = month(fast_strptime(release_month, format = "%b"), label =
                                 TRUE)) %>%
  mutate(release_month = factor(release_month, levels = month.abb, ordered = FALSE))
```

```{r}
test_data_cleaned <- test_data_cleaned %>%
  mutate(movie_budget = as.numeric(str_replace_all(movie_budget, ",", "")))
```


```{r}
test_data_cleaned <- test_data_cleaned %>%
  mutate(across(
    .cols = c(
      "movie_budget",
      'duration',
      'nb_news_articles',
      'actor1_star_meter',
      'actor2_star_meter',
      'actor3_star_meter',
      'nb_faces',
      'movie_meter_IMDBpro'
    ),
    .fns = ~ scale(.) %>% as.vector()
  ))
```

```{r}
for (keyword in top_10_keywords$plot_keywords) {
  col_name <- glue("plot_{keyword}")
  test_data_cleaned[[col_name]] <-
    as.integer(lapply(test_data_cleaned$plot_keywords, function (x) {
      str_detect(x, keyword)
    }))
}

for (distributor in top_5_distributors$distributor) {
  col_name <- glue("distributor_{distributor}")
  test_data_cleaned[[col_name]] <-
    as.integer(lapply(test_data_cleaned$distributor, function (x) {
      str_detect(x, distributor)
    }))
}
```

```{r}
columns_to_remove <-
  c(
    "movie_id",
    "movie_title",
    "imdb_link",
    "actor1",
    "actor2",
    "actor3",
    "genres",
    "release_year",
    "colour_film",
    'actor1_star_meter',
    'actor2_star_meter',
    'actor3_star_meter',
    "director",
    "cinematographer",
    "production_company",
    "language",
    "country",
    "distributor",
    "plot_keywords"
  )

test_data_cleaned <- test_data_cleaned %>% select(-all_of(columns_to_remove))
```

```{r}
test_data_cleaned
```
## Predicting ratings of new movies
```{r warning=FALSE}
lin_reg_predict <- as.data.frame(predict(lin_reg_k, test_data_cleaned))
poly_reg_predict <- as.data.frame(predict(poly_k_fold, test_data_cleaned))
spline_reg_predict <- as.data.frame(predict(spline_model_1, test_data_cleaned))

predictions <-
  data.frame(
    test_data$movie_title,
    dmy(
      str_c(
        test_data$release_day,
        test_data$release_month,
        test_data$release_year,
        sep = "-"
      )
    ),
    lin_reg_predict,
    poly_reg_predict,
    spline_reg_predict
  )


names(predictions) <- c("Movie Title", "Release Date" ,"Linear", "Polynomial", "Spline")

predictions
```
```{r}
stargazer(predictions, header = FALSE, digits = 2, type = "latex", out = "tables/predictions.html", summary = FALSE, title = "Model predictions")
```

## Running ANOVA
```{r}
anova(lin_reg_k, poly_k_fold, spline_model_1, test = "F")
```
From the ANOVA, we see that the spline regression model has the lowest residuals. However, when we check the predictions, we see that the spline model actually provides a rating outside the boundary of 0-10. Therefore, we decide to go with the polynomial regression model as our final model.

# Presenting the final model
```{r warning=FALSE}
names(poly_k_fold$coefficients) <- c(
  "Intercept",
  "Movie Budget",
  "Duration",
  "Duration^2",
  "News Articles",
  "News Articles^2",
  "News Articles^3",
  "News Articles^4",
  "IMDB Pro Meter",
  "IMDB Pro Meter^2",
  "IMDB Pro Meter^3",
  "IMDB Pro Meter^4",
  "IMDB Pro Meter^5",
  "Released in February",
  "Released in March",
  "Released in April",
  "Released in May",
  "Released in June",
  "Released in July",
  "Released in August",
  "Released in September",
  "Released in October",
  "Released in November",
  "Released in December",
  "G Rating",
  "PG Rating",
  "PG-13 Rating",
  "R Rating",
  "Other Maturity Rating",
  "Aspect Ratio 1.85",
  "Aspect Ratio 2.35",
  "Other Aspect Ratio",
  "Number of Faces in Poster",
  "Action",
  "Adventure",
  "Sci-Fi",
  "Thriller",
  "Musical",
  "Romance",
  "Western",
  "Sport",
  "Horror",
  "Drama",
  "War",
  "Animation",
  "Crime",
  "Plot = Murder",
  "Plot = Love",
  "Plot = Friends",
  "Plot = Death",
  "Plot = High School",
  "Plot = Police",
  "Plot = New York City",
  "Plot = a Boy",
  "Plot = Drugs",
  "Plot = School",
  "Distributor = Warner Bros.",
  "Distributor = Universal Pictures",
  "Distributor = Paramount Pictures",
  "Distributor = Twentieth Century Fox",
  "Distributor = Columbia Pictures Corporation"
)

coeftest(poly_k_fold, vcov = vcovHC(poly_k_fold, type = "HC1")) %>%
  stargazer(
    header = FALSE,
    digits = 2,
    type = "latex",
    out = "tables/polynomial_regression_summary.html",
    title = "Polynomial regression"
  )
```
